What's in a Domain? Analysis of URL Features

### 2023-07-03 paper/paper.tex
Paper
Paper revisions - following reviewer feedback - DSCC 2023

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2022}
\acmYear{2022}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation emai}{June 03--05,
  2022}{Austin, TX}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% For managing citations, it is recommended to use bibliography
%% files in BibTeX format.
%%
%% You can then either use BibTeX with the ACM-Reference-Format style,
%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
%% support for advanced citation of software artefact from the
%% biblatex-software package, also separately available on CTAN.
%%
%% Look at the sample-*-biblatex.tex files for templates showcasing
%% the biblatex styles.
%%

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{What's in a Domain? Anaylsis of URL Features}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{John Hawkins}
\email{john.hawkins@Getting-Data-Science-Done.com}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Getting-Data-Science-Done.com}
  \city{Sydney}
  \state{NSW}
  \country{Australia}
  \postcode{2000}
}

\renewcommand{\shortauthors}{Hawkins}

\begin{abstract}
Many data science problems require processing log data derived from web pages, apis or other
internet traffic sources. URLs are one of the few ubiquitous data fields that describe
internet activity, hence they require effective processing for a wide variety of machine 
learning applications. While URLs are structurally rich, the structure can be both domain specific
and subject to change over time, making feature engineering for URLs an ongoing challenge.

In this research we outline the key structural components of URLs and discuss the information
available within each. We describe methods for generating features on these URL components and 
share an open source implementation of these ideas. In addition, we describe a method for 
exploring URL feature impact that allows for comparison and analysis of the information available inside URLS.
We experiment with a collection of URL classification problems and demonstrate their utility 
of these tools. 
\end{abstract}
% https://pypi.org/project/url2features

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002951.10003260.10003261</concept_id>
<concept_desc>Information systems~Web searching and information discovery</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10002951.10003260.10003277.10003280</concept_id>
<concept_desc>Information systems~Web log analysis</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010257</concept_id>
<concept_desc>Computing methodologies~Machine learning</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Web searching and information discovery}
\ccsdesc[500]{Information systems~Web log analysis}
\ccsdesc[500]{Computing methodologies~Machine learning}

\keywords{URL Features, Document Classification, Machine Learning, Semantic Web}

@@

@@

The Uniform Resource Locator (URL) is a ubiquitous element the digital world. 
We use them to retrieve news and media, advertise or find businesses and services, 
and to interact with other people across a broad of social applications. Below the
surface many online services use URLs internally for communicating with other digital
services, making the URL a fundamental data point for both users and machines.

@@

The URL is made up of multiple elements, but at its core is the domain. The domain
contains internal information about both the intended purpose of a URL, its legitimacy 
and the likely country of origin. The domain is also a source of additional information 
through requests to Domain Name Servers (DNS) to understand both its history and structure
 of its network topology and resources.

Beyond the domain, the URL consists of a sequence of words, categories, identfiers, dates
or domain specific abreviations. This sequence can indicate the psychoogical elements of how
information is categeoried, or the internal logic of an application that generates or presents
content dynamically.

\begin{figure*}
\centering
\includegraphics[scale=0.6]{images/URL_parts.png}
\caption{Structural components of a URL requiring specific feature engineering treatment}
\label{fig:url_structure}
\end{figure*}

@@

Some authors have 
emphasized that URLs are sequences of characters and require feature extraction methods that respect 
this sequential nature\cite{Le2018,Vazhayil2018}. They have naturally turned to developing neural network approaches
based on convolutional or recurrent layers for learning these sequential structures.
However, the ordering of key features within URLs is predominantly fixed as shown in Figure \ref{fig:url_structure}.
The core elements of URL structure occur at fixed positions within the sequence, in contrast to human language
sequences which are built from flexible grammars that allow variable positioning of most key elements. The
inherent structure of URLs has been shown to be a source of information that can be exploited in 
algorithm design \cite{Shih2004}. Furthermore,
there are psychological and social elements to URL construction (such as the use of common brand names in subdomains
for phishing attack URLS \cite{Tupsamudre2019}), which emphasize the utility of feature engineering techniques that
respect the inherent structure of URLs.

Typically, researchers employ feature engineering strategies exploit these potential sources of information
in ways that are appropriate for a given task. However, while there are wide variety
of approaches that are inconsistently applied, there have been limited studies into
the overall effectiveness of different strategies across a range of applications.

In this work we develop a feature engineering library that maintains an ontology of URL features
related to underlying structure of the URL. In addition we provide a method for visualising the importance of features
across the URL structure. These techniques can prove useful for analysing features for problems that
consist of moving targets and require broad sets of potential features and efficient feature selection \cite{Basnet2012}.
We then present an open source package for generating features within these
ontologocal classes and apply them to a variety of tasks. We present our results as a
cross-task evaluation of URL features.

@@

The structural components of a URL shown in Figure \ref{fig:url_structure} are tabulated with an overview of both
the information source in those components are potenital issues with feature engineering in Table \ref{tab:components}

\begin{table*}
\caption{URL Components and Feature Information}
\label{tab:components}
\begin{tabular}{|l|l|l|}
\toprule
Component    &Subcomponent      &Type of Feature Information       \\
\midrule
Protocol     &                  &Type of content, technology, security of transmission             \\
\midrule
Domain       &                  &Textual data indicating general purpose      \\
             &Subdomain         &Specific purpose or categorisation of content           \\
             &Top Level Domain  &Business or service purpose, authenticty, geograpahy, age           \\
\midrule
Path         &                  &Content structure, file or operation system, application type or structure         \\
\midrule
File         &                  &Naming of specific content, psychological intent, executable or static types      \\
\midrule
Parameters   &                  &Substructure of content, personalization, security, tracking         \\
             &Keys              &Set of categories used to differentiate substructure        \\
             &Values            &Set of values for substructure, indication of page content        \\
             &Fragment          &Labels for specifc substructure, source of new application customisation        \\
\bottomrule
\end{tabular}
\end{table*}

We design a feature extraction library for URLs that generates features specific to each component of the
URL indepenently and using an naming convention that permits sepearation and grouping for analysis.
Previous work has presented datasets for specific problems where the features
are provided with a similar structural grouping\cite{Vrban2020}. However, we provide our feature extraction
application designed so that any specific subset of these features can be extracted and analysed 
for a specific task.

We apply this library to multiple machine learning tasks using only URLs as the input variable. We choose
these tasks such that they span very different classes of problems an dataset sizes. 
We experiment with multiple standard machine learning techniques and evaluate
the impact of the URL features using the SHAP package for feature importance. We develop a process
for analysing thess features within the logical structure of the URL.

@@

\begin{table}
\caption{Datasets}
\label{tab:data}
\begin{tabular}{|l|r|r|r|}
\toprule
Dataset              &Records        &Classes  &Majority    \\
\midrule
spam                 &47,378          &2       &75\%        \\
Malware              &46,944          &2       &75\%        \\
Phishing             &45,343          &2       &78\%        \\
WebKb 4Uni           &8,284           &7       &45\%        \\
Syskill \& Webert    &330             &3       &68\%        \\
DMOZ                 &1,562,978       &15      &16\%        \\
\bottomrule
\end{tabular}
\end{table}

@@

@@

@@

\subsection{Features}

We generate URL features in groups that focus on distinct regions across the URL. We create a group
of global features that contain general string properties of the entire URL, then create regions
specific features as outlined in Table \ref{tab:features}.

@@

@@

We use the SHAP\cite{Lundberg2017} package to calculate feature importance using a small holdout test set 
of 80-100 smaples per experiment. We aggregate the shapley values for these sample points to calculate the mean
absolute contribution of each feature, as is typically done in Shaplet fetaure importance plots.

For our URL feature analysis, we then group these individual feature importance values by the specific URL segment
that the feature was derive from, using Figure \ref{fig:url} as a guide to these segments. 
We sum the feature importance for all features within a URL segment to allow us to plot the
segment contributions to model performance. We provide a thin grey coloured line covering the entire segment
which captures the importance of global features (like URL length). If the script is applied to a dataset with
more than just URL features then all non-URL fetaures would be grouped into this global group. All segment specific
URL features are plotted below their segment in a canonical example URL.

These plots allow for structural understanding of how URL data
controbutes to predictive performance of a model and permits the comparison of feature importance 
across the five problems in this study. The script for generating these plots is provides as part of the
`url2features` open source package.

@@

A set of standard machine learning pipelines are applied to each of the four problems. Each approach is applied
using default parameters, without any fine tuning. We use feature preprocessing modules appropriate for each class
of model. All details are available in the source repository for the experiments. The performance of the models
is tabulated in Table \ref{tab:results}, where we show Balanced Accuracy of each model on the holdout data, as this
metric is appropriate and comparable across all six problems.

\begin{table}
\caption{Machine Learning Results}
\label{tab:results}
\begin{tabular}{|l|r|r|r|r|}
\toprule
Dataset              &NB     &LR    &XT    &LGBM     \\
\midrule
Spam                 &1.00   &1.00  &1.00  &1.00     \\
Malware              &0.65   &0.93  &0.99  &1.00     \\
Phishing             &0.89   &0.98  &0.99  &1.00     \\
WebKb 4Uni           &0.30   &0.36  &0.58  &0.49     \\
Syskill \& Webert    &0.39   &0.35  &0.37  &0.33     \\
DMOZ                 &0.12   &0.17  &0.29  &0.25     \\
\bottomrule
\end{tabular}
\end{table}

\begin{figure*}
\centering
\includegraphics[scale=0.8]{images/URL_importance.png}
\caption{Structural Depiction of URL Feature Importance}
\label{fig:importance}
\end{figure*}

The table of results indicates that internet security problems appear much more amenable to URL based 
classification. All three of these problems result in high performing classifiers. In comparison the topic
and user preference based tasks achieve far more modest performance. It is worth noting that these problems 
are hindered by both higher cardinality targets and greater variability in dataset size, 2 of the 3 data 
sets are much smaller than any of the security datasets. However, the performance on the very large DMOZ
dataset strongly suggests that, in general, URL based topic classification is likely to remain a difficult
problem.

@@

We see that there is substantial variability across all classification tasks in these experiments.
The protocol and parameters sections remain mostly devoid of signal, with the exception of the Spam URL classifcation
task, where we see some value in the URL parameter features. The domain, path and file regions are the predominant sources
of signal across these tasks. Nevertheless, the emphasis changes between them. The subdomain appears particularly
important for the phishing URL identfication, whereas the URL target file is the focus for the WebKb classifciation data.

@@

\section{Acknowledgments}

\bibliographystyle{ACM-Reference-Format}
\bibliography{refs}

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.

>>>>

\documentclass{aircc}
\usepackage{mathpartir}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{geometry}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{anyfontsize}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
\lstset{style=mystyle}

\begin{document}

\title{What's in a Domain? Analysis of URL Features}

\author{John Hawkins}
\affiliation{Getting-data-science-done.com}
\affiliation{Transitional AI Research Group}

@@

\begin{abstract}
Many data science problems require processing log data derived from web pages, APIs or other
internet traffic sources. URLs are one of the few ubiquitous data fields that describe
internet activity, hence they require effective processing for a wide variety of machine 
learning applications. While URLs are structurally rich, the structure can be both domain specific
and subject to change over time, making feature engineering for URLs an ongoing challenge.

In this research we outline the key structural components of URLs and discuss the information
available within each. We describe methods for generating features on these URL components and 
share an open source implementation of these ideas. In addition, we describe a method for 
exploring URL feature importance that allows for comparison and analysis of the information 
available inside URLs.
We experiment with a collection of URL classification datasets and demonstrate the utility 
of these tools. Package and source code is open on \textit{https://pypi.org/project/url2features}
\end{abstract}

\begin{keywords}
Machine Learning, Feature Engineering, Web Search, Semantic Web, Data Science
\end{keywords}

@@

The Uniform Resource Locator (URL) is a ubiquitous element in the digital world. 
We use them to retrieve news and media, advertise or find businesses and services, 
and to interact with other people across a broad range of social applications. Below the
surface many online services use URLs internally for communicating with other digital
services, making the URL a fundamental data point for both users and machines.

@@

The URL is made up of multiple elements, but at its core is the domain. The domain
contains internal information about both the intended purpose of a URL, its legitimacy 
and the likely country of origin. The domain is also a source of additional information 
through requests to Domain Name Servers (DNS) to understand both its history and the
structure of its network topology and resources.

Beyond the domain, the URL consists of a sequence of words, categories, identfiers, dates
or domain specific abreviations. This sequence can indicate the psychological elements of how
information is categeoried, or the internal logic of an application that generates or presents
content dynamically.

\begin{figure*}
\centering
\resizebox{\columnwidth}{!}{%
\includegraphics[scale=0.6]{images/URL_parts.png}
}
\caption{Structural components of a URL requiring specific feature engineering treatment}
\label{fig:url_structure}
\end{figure*}

@@

Some authors have 
emphasized that URLs are sequences of characters and require feature extraction methods that respect 
this sequential nature\cite{Le2018,Vazhayil2018}. They have naturally turned to developing neural network approaches
based on convolutional or recurrent layers for learning these sequential structures.
However, the ordering of key features within URLs is predominantly fixed as shown in Figure \ref{fig:url_structure}.
The core elements of URL structure occur at fixed positions within the sequence, in contrast to human language
sequences which are built from flexible grammars that allow variable positioning of most key elements. The
inherent structure of URLs has been demonstrated to be a source of information that can be exploited in 
algorithm design \cite{Shih2004}. Furthermore,
there are psychological and social elements to URL construction (such as the use of common brand names in subdomains
for phishing attack URLS \cite{Tupsamudre2019}), which emphasize the utility of feature engineering techniques that
respect the inherent structure of URLs.

Typically, researchers employ feature engineering strategies to exploit these potential sources of information
in ways that are appropriate for a given task. However, while there are wide variety
of approaches that are inconsistently applied, there have been limited studies into
the overall effectiveness of different strategies across a range of applications.

In this work we develop a feature engineering library that maintains an ontology of URL features
related to underlying structure of the URL. In addition we provide a method for visualising the importance of features
across the URL structure. These techniques can prove useful for analysing features for problems that
consist of moving targets and require broad sets of potential features and efficient feature selection \cite{Basnet2012}.
We then present an open source package for generating features within these
ontologocal classes and apply them to a variety of tasks. We present our results as a
cross-task evaluation of URL features. The strength of our approach lies in the ability to both understand how
machine learning models use URLs in decision making, this is opposed to the black-box problem with neural network
models that treat the URL as a text sequence. In addition, the cross-task evaluation we perform provides insight into
what works within different domains. This is critical as many machine learning problems that rely on URLS require
models built on relatively small datasets, so that new patterns of fraud and behaviour can be reacted to in a timely
fashion.

@@

The structural components of a URL (as illustrated in Figure \ref{fig:url_structure}) are listed in Table \ref{tab:components}.
We include an overview the information source in each of those components and highlight how these components relate to
functional machine learning features.

\begin{table*}
\caption{URL Components and Feature Information}
\label{tab:components}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{|l|l|l|}
\toprule
Component    &Subcomponent      &Type of Feature Information       \\
\midrule
Protocol     &                  &Type of content, technology, security of transmission             \\
\midrule
Domain       &                  &Textual data indicating general purpose      \\
             &Subdomain         &Specific purpose or categorisation of content           \\
             &Top Level Domain  &Business or service purpose, authenticty, geograpahy, age           \\
\midrule
Path         &                  &Content structure, file or operation system, application type or structure         \\
\midrule
File         &                  &Naming of specific content, psychological intent, executable or static types      \\
\midrule
Parameters   &                  &Substructure of content, personalization, security, tracking         \\
             &Keys              &Set of categories used to differentiate substructure        \\
             &Values            &Set of values for substructure, indication of page content        \\
             &Fragment          &Labels for specifc substructure, source of new application customisation        \\
\bottomrule
\end{tabular}
}
\end{table*}

We design a feature extraction library for URLs that generates features specific to each component of the
URL independently using a naming convention that permits sepearation and grouping for analysis.
Previous work has presented datasets for specific problems where the features
are provided with a similar structural grouping\cite{Vrban2020}. However, we provide our feature extraction
application designed so that any specific subset of these features can be extracted and analysed 
for a specific task.

We apply this library to multiple machine learning tasks using only URLs as the input variable. We choose
these tasks such that they span very different classes of problems and dataset sizes. 
We experiment with multiple standard machine learning techniques and evaluate
the impact of the URL features using the SHAP package for feature importance. We develop a process
for analysing these features within the logical structure of the URL.

@@

\begin{table}
\caption{Datasets}
\fontsize{3pt}{3pt}\selectfont
\label{tab:data}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{|l|r|r|r|}
\toprule
Dataset              &Records        &Classes  &Majority    \\
\midrule
spam                 &47,378          &2       &75\%        \\
Malware              &46,944          &2       &75\%        \\
Phishing             &45,343          &2       &78\%        \\
WebKb 4Uni           &8,284           &7       &45\%        \\
Syskill \& Webert    &330             &3       &68\%        \\
DMOZ                 &1,562,978       &15      &16\%        \\
\bottomrule
\end{tabular}
}
\end{table}

@@

\resizebox{\columnwidth}{!}{%

@@

}

@@

\subsection{Feature Generation}

We generate URL features using a set of functions that focus on distinct types of features applied to specific 
regions across the URL. This permits users to apply subsets of functions that define only the features they
require. In addition we create a group of global features that contain general string properties of the entire 
URL, rather than specific regions. The complete set of features, along with their categorisation and definition
are outlined in Table \ref{tab:features}.

@@

\begin{lstlisting}[language=Bash,label={code:cli}, caption=Install and invoke the url2features package from CLI]
pip install url2features
url2features -columns=URLCOL -host -tld input.csv > output.csv
\end{lstlisting}

The commands for installing and invoking the \emph{url2features} package from the command line are shown
in Listing \ref{code:cli}. 
When execting this code it will take the tabular data inside the file \emph{input.csv} and then apply feature 
engineering on the column named \emph{URLCOL}. The features to be created are defined by the switches 
$-host$ and $-tld$ for the host and top level domain features. By default the application outputs to
STDOUT, so in this example we are redirecting the output of the program to create a new file \emph{output.csv}.

\begin{lstlisting}[language=Python,label={code:skl}, caption=Usage of url2features with scikit-learn pipelines ]
from url2features.pipeline import URLTransform
from sklearn.linear_model import SGDClassifier
from sklearn.pipeline import Pipeline

pipeline = Pipeline([
    ('urltransform', URLTransform(['URLCOL'],['host','tld']) ),
    ('clf', SGDClassifier(loss='log') ),
])
\end{lstlisting}

The package can also be invoked programmatically and included inside a machine learning framework like 
scikit-learn pipelines\cite{pedregosa2011scikit}. This is shown in Listing \ref{code:skl}, where the
same two feature engineering functions (host and tld) are included as feature transformers in a machine 
learning pipeline. The advantage of this approach is that these transformations can be built into a single
serialised model for deployment.

@@

We use the SHAP\cite{Lundberg2017} package to calculate feature importance using a small holdout test set 
of 80-100 samples per experiment. We aggregate the Shapley values for these sample points to calculate the mean
absolute contribution of each feature, as is typically done in Shapley feature importance plots.

For our URL feature analysis, we then group these individual feature importance values by the specific URL segment
that the feature was derived from, using Figure \ref{fig:url_structure} as a guide to these segments. 
We sum the feature importance for all features within a URL segment to allow us to plot the
segment contributions to model performance. We provide a thin grey coloured line covering the entire segment
which captures the importance of global features (like URL length). If the script is applied to a dataset with
more than just URL features then all non-URL fetaures would be grouped into this global group. All segment specific
URL features are plotted below their segment in a canonical example URL.

These plots allow for a structural understanding of how URL data
contributes to predictive performance of a model and permits the comparison of feature importance 
across the six problems in this study. The script for generating these plots is provided as part 
of the source code for the `url2features` package.

@@

A set of standard machine learning pipelines are applied to each of the six problems. Each approach is applied
using default parameters, without any fine tuning. We use feature preprocessing modules appropriate for each class
of model. All details are available in the source repository for the experiments. The performance of the models
is shown in Table \ref{tab:results}, where we show Balanced Accuracy of each model on the holdout data, as this
metric is appropriate and comparable across all six problems.

\begin{table}
\caption{Machine Learning Results}
\fontsize{3pt}{3pt}\selectfont
\label{tab:results}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{|l|r|r|r|r|}
\toprule
Dataset              &NB     &LR    &XT    &LGBM     \\
\midrule
Spam                 &1.00   &1.00  &1.00  &1.00     \\
Malware              &0.65   &0.93  &0.99  &1.00     \\
Phishing             &0.89   &0.98  &0.99  &1.00     \\
WebKb 4Uni           &0.30   &0.36  &0.58  &0.49     \\
Syskill \& Webert    &0.39   &0.35  &0.37  &0.33     \\
DMOZ                 &0.12   &0.17  &0.29  &0.25     \\
\bottomrule
\end{tabular}
}
\end{table}

\begin{figure*}
\centering
\resizebox{\columnwidth}{!}{%
\includegraphics[scale=0.8]{images/URL_importance.png}
}
\caption{Structural Depiction of URL Feature Importance}
\label{fig:importance}
\end{figure*}

The table of results indicates that internet security problems appear much more amenable to URL based 
classification. All three of these problems result in high performing classifiers. In comparison the topic
and user preference based tasks achieve far more modest performance. It is worth noting that these problems 
are hindered by both higher cardinality in the classification targets and greater variability in dataset size,
 2 of the 3 data sets are much smaller than any of the security datasets. However, the performance on the very large DMOZ
dataset strongly suggests that, in general, URL based topic classification is likely to remain a difficult
problem.

@@

We see that there is substantial variability across all classification tasks in these experiments.
The protocol and parameters sections remain mostly devoid of signal, with the exception of the Spam URL classification
task, where we see value in the URL parameter features. The domain, path and file regions are the predominant sources
of signal across these tasks. Nevertheless, the emphasis changes between them. The subdomain appears particularly
important for the phishing URL identfication, whereas the URL target file is the focus for the WebKb classification data.

@@

\bibliographystyle{ieeetr}
\bibliography{refs}

\end{document}
\endinput
